### 2015-12-09 AssignmentVIII/Assignment8-Ditz_Schroeder-WS15-16.tex
anfänge des achten übungsblattes

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
\usepackage{TikZ} %phylogenetischer Baum
\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
\usetikzlibrary{automata,arrows}
\usepackage{subfigure}

@@

\newcommand{\points}[1]{
\newcounter{colmns}
\setcounter{colmns}{#1}
\stepcounter{colmns}
  \begin{vartab}{\thecolmns}
    \numbers{#1} & $\sum$\\\hline
    \emptyLine{\thecolmns}\\
  \end{vartab}
}

\begin{document}
%\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
\header{7}{Alexander Seitz}{26. October 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}

 \section*{Exercise 1 - \textsl{Hirschberg algorithm for alignment in linear space}}

 \section*{Exercise 2 - \textsl{Do scoring matrices have expected score smaller than zero?}}

 \section*{Exercise 3 - \textsl{Needleman-Wunsch algorithm for affine gap scores}}

>>>>

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
%\usepackage{TikZ} %phylogenetischer Baum
%\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
%\usetikzlibrary{automata,arrows}
\usepackage{subfigure}

@@

\newcommand{\points}[1]{
\newcounter{colmns}
\setcounter{colmns}{#1}
\stepcounter{colmns}
  \begin{vartab}{\thecolmns}
    \numbers{#1} & $\sum$ (6+2)\\\hline
    \emptyLine{\thecolmns}\\
  \end{vartab}
}

\begin{document}
%\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
\header{8}{Alexander Seitz}{14. December 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}

\section*{Theoretical Assignment - \textit{Suffix tree construction and application}}

\subsection*{a - \textit{Suffix tree construction}}
\subsubsection*{i}
If one uses the naive approach to construct the suffix tree of ``CTAGTAGCAG'', the result would look 
like Figure \ref{fig:naiveImpl}.

\begin{figure}[ht]
 \centering
 \subfigure[step 1]{
  \includegraphics[width=0.15\textwidth]{tast1ai/tree_step01.png}
 }
 \subfigure[step 2]{
  \includegraphics[width=0.25\textwidth]{tast1ai/tree_step02.png}
 }
 \subfigure[step 3]{
  \includegraphics[width=0.35\textwidth]{tast1ai/tree_step03.png}
 }
 \subfigure[step 4]{
  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step04.png}
 }
 \subfigure[step 5]{
  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step05.png}
 }
 \subfigure[step 6]{
  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step06.png}
 }
 \subfigure[step 7]{
  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step07.png}
 }
 \subfigure[step 8]{
  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step08.png}
 }
 \subfigure[step 9]{
  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step09.png}
 }
 \subfigure[step 10]{
  \includegraphics[width=0.7\textwidth]{tast1ai/tree_step10.png}
 }
 \subfigure[step 11]{
  \includegraphics[width=0.7\textwidth]{tast1ai/tree_step11.png}
 }
 \caption{All steps of the naive implementation of suffix tree construction for the string ``CTAGTAGCAG''.}
 \label{fig:naiveImpl}
\end{figure}

\subsubsection*{ii}

\subsection*{b - \textit{Main data table of WOTD}}

\subsection*{c - \textit{Suffix tree application}}

\section*{Theoretical Assignment - \textit{Runtime and space complexity of suffix trees}}

\subsection*{a}

\subsection*{b}

\subsection*{c}
